COVID-19 dataset strength

### 2021-05-08 old/covid_dataset_strength/covid_dataset_strength.Rmd
Move obsolete files to 'old' folder

```{r}
t <- tibble::tibble(
  prot_name = as.character(
    na.omit(
      stringr::str_match(
        names(sequences),
        "^([:upper:][:alnum:]{0,5})\\|"
      )[, 2]
    )
  ),
  sequence = as.character(sequences)
)
library(dplyr)
t$prot_name <- as.factor(t$prot_name)
t_unique <- t %>% group_by(prot_name) %>% 
  summarise(n = n(), n_distinct = n_distinct(sequence)) %>%
  mutate(perc = n_distinct / n)
perc_unique <- mean(t_unique$perc)
```

Of all proteins, on average, `r perc_unique` are unique.

```{r}
n_unique_sequences <- perc_unique * n_sequences
```

>>>>

```{r}
t <- tibble::tibble(
  prot_name = as.character(
    na.omit(
      stringr::str_match(
        names(sequences),
        "^([:upper:][:alnum:]{0,5})\\|"
      )[, 2]
    )
  ),
  sequence = as.character(sequences)
)
library(dplyr)
t$prot_name <- as.factor(t$prot_name)
t_unique <- t %>% group_by(prot_name) %>% 
  summarise(n = n(), n_distinct = n_distinct(sequence)) %>%
  mutate(perc = n_distinct / n)
perc_unique_protein <- mean(t_unique$perc)
```

Of all proteins, on average, `r perc_unique_protein` are unique.
We are looking, however, for unique proteomes. The percentage
of unique proteomes is the product of

```{r}
percs_duplicate_protein <- 1.0 - t_unique$perc
perc_duplicate_proteome <- prod(percs_duplicate_protein)
perc_unique_proteome <- 1.0 - perc_duplicate_proteome
```

```{r}
n_unique_sequences <- perc_unique_proteome * n_sequences
```
